Design/Cybernetics: Two Sides of One Coin

### 2019-10-31 MSC-ReadingCourse.tex
add intro

\begin{frame}
	\textit{\rm``The progress of knowledge is at the same time the progress of ignorance.''}\\
	--- Edgar Morin \cite{morin_1992} \\
	\vspace{0.4cm}
	\textit{\rm``The very act of focusing prevents us from seeing.''}\\
	--- ?? \\
	\vspace{0.4cm}
	\textit{\rm``We do not see what we do not see, and what we do not see does not exist.''}\\
	--- Humberto R. Maturana and Francisco J. Varela \cite{maturana_varela_1987}\\
	\vspace{0.4cm}
	\textit{\rm``The only way to overcome second-order deficiencies is with therapies of second order.''}\\
	--- Heinz von Foerster \cite{vonFoerster_2003}\\
	\vspace{0.4cm}
	\begin{figure}
		\centering
		\href{https://anewage.github.io}{
			\includegraphics[width=2cm]{resources/anewage_github_io.png}
		}
	\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Prologue II}
	{\textbf{Gödel's incompleteness} theorems can be summarized as: \\
		It is impossible to construct a theoretical language that will not \textcolor{teal}{close on itself}, with the result that there are statements that are \textcolor{teal}{undecidable} in that language.} \\
	\vspace{0.5cm}
	{In other words: There are things that you \textcolor{teal}{cannot explain within a paricular language}.}

@@

\section{Introduction}
	\subsection{Definitions}
		\begin{frame}
%			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics}
			\framesubtitle{The Root of the Word}
			\textbf{Cybernetics} (\textbackslash \textipa{saI\texttt{}b@r"netIks}\textbackslash):
			\begin{itemize}
				\item<1-> From Greek `kybernetes': `\textcolor{teal}{steersman}', `kybernan': `to steer or pilot a ship, direct as a pilot'
				\item<2-> Is about having a goal and taking action to achieve that goal
				\item<3-> The art of steering \cite{pangaro_web}:
			\end{itemize}
			\centering\includegraphics<3>[width=7.2cm]{./resources/steering1.png}
			\centering\includegraphics<4>[width=7.2cm]{./resources/steering2.png}
			\centering\includegraphics<5>[width=7.2cm]{./resources/steering3.png}
			\centering\includegraphics<6>[width=7.2cm]{./resources/steering4.png}
			\centering\includegraphics<7>[width=7.2cm]{./resources/steering5.png}
			\centering\includegraphics<8>[width=7.2cm]{./resources/steering6.png}
			\centering\includegraphics<9>[width=7.2cm]{./resources/steering7.png}
			\centering\includegraphics<10>[width=7.2cm]{./resources/steering8.png}
			\centering\includegraphics<11>[width=7.2cm]{./resources/steering9.png}
			\centering\includegraphics<12>[width=7.2cm]{./resources/steering10.png}

%			\setbeamercovered{invisible}
		\end{frame}
		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Soooo... What is Cybernetics?}
			\begin{itemize}
				\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
				--- Plato
				\item<2->``Cybernetique is the art of governing or the science of government.''\\
				--- André-Marie Ampère
				\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
				Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
				\item<4->``The Science of Effective Organization''\\
				--- Stafford Beer
				\item<5->``The art and science of uderstanding.''\\
				--- Humerto Maturana
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Soooo... What is Cybernetics?}
			\begin{itemize}
				\item<1->``The art and science of manipulating defensible metaphors''
				--- Gordon Pask
				\item<2->``A form of cross-disciplinary thought which made it possible for members of many disciplines to communicate with each other easily in a language which all could understand''
				--- Margaret Mead
				\item<3->``That is the fascinating thing about cybernetics. You ask a couple of people to give you a definition and although you don’t get to know much about cybernetics from them, you find out a lot about the person supplying the definition, including their area of expertise, their relation to the world, their desire to play with metaphors, their enthusiasm for management, and their interest in communications or message theory.''\\
				--- Heinz von Foerster
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Soooo... What is Cybernetics?}
			\begin{itemize}
				\item A clear-cut and crisp definition is very hard to find.
				\item An entire webpage is dedicated for different definitions: \url{http://asc-cybernetics.org/definitions/}\\
			\end{itemize}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Will History Help?}
			\begin{itemize}
				\item<1->The storylines do not split into distinct lines of descent.
				\item<2->The storylines do not subdivide into clear phases or stages.
				\item<3->\textcolor{red}{Cybernetics' history defies neat categories and compartments}...
				\item<4->An entire webpage and a lot of diagrams can be found about the history of Cybernetics: \url{http://www.asc-cybernetics.org/foundations/timeline.htm}
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{What About Ven Diagram, Set Theory, or Any Other Categoriazation Method?!}
			\begin{itemize}
				\item<1->Everybody has a different opinion as to Cybernetics' disciplinary `slot'.
				\item<2->Each person involved in Cybernetics research, draws a new line on the territory of Cybernetics. Therefore Any map of relevant people and their timeline will fail to show the exact contexts.
				\item<3->... \textcolor{red}{Cybernetics defies neat categories and compartments}
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Cybernetics defies neat categories and compartments}
			\centering\includegraphics[height=0.7\textheight]{./resources/frustrated.png}
		\end{frame}

	\subsection{Background}
		\begin{frame}
		\frametitle{Background and Theme}
		\framesubtitle{Automaticity of Behaviour in Artificial Objects}
			\begin{columns}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=3cm]{./resources/chinesecompasscart.jpg}
					\caption{Chinese Compass Cart}
				\end{figure}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=2cm]{./resources/waterclock.jpg}
					\caption{Ctesibius's Water Clock - 300s B.C.}
				\end{figure}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=3.5cm]{./resources/flyball.png}
					\caption{James Watt's Flyball Governor - 1780s}
				\end{figure}
			\end{columns}
			\begin{itemize}
				\item<1->All tools incorporated \textcolor{teal}{self-regulating} behavior without so much attention to a specific theory.
			\end{itemize}
		\end{frame}

\section{Proposal}
\subsection{Methodology}
\begin{frame}
\frametitle{Step 1}
\framesubtitle{Overall view}
	\begin{itemize}
		\item<1->The first
		\item<2->The second
		\item<3->The last
	\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Step 1 (Cont'd)}
\framesubtitle{Aspects}
\begin{enumerate}
	\item<1->The first
	\item<2->The second
	\item<3->The last
\end{enumerate}
\end{frame}
\section{References}
	\begin{frame}[t,allowframebreaks]
		\frametitle{References}
		\printbibliography
	\end{frame}

\section*{Appendix}
	\begin{frame}
		\setbeamercovered{transparent}
		\frametitle{Definition(s) of Cybernetics}
		\framesubtitle{Soooo... What is Cybernetics?}
		\begin{itemize}
			\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
			--- Plato (420s-340s B.C.)
			\item<2->``Cybernetique is the art of governing or the science of government.''\\
			--- André-Marie Ampère (1775-1836)
			\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
			Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
		\end{itemize}
		\setbeamercovered{invisible}
	\end{frame}

>>>>

    \begin{frame}
    	\textit{\rm``The progress of knowledge is at the same time the progress of ignorance.''}\\
    	--- Edgar Morin \cite{morin_1992} \\
    	\vspace{0.4cm}
    	\textit{\rm``The very act of focusing prevents us from seeing.''}\\
    	--- ?? \\
    	\vspace{0.4cm}
    	\textit{\rm``We do not see what we do not see, and what we do not see seems nonexistent.''}\\
    	--- Humberto R. Maturana and Francisco J. Varela \cite{maturana_varela_1987}\\
    	\vspace{0.4cm}
    	\textit{\rm``The only way to overcome second-order deficiencies is with therapies of second order.''}\\
    	--- Heinz von Foerster \cite{vonFoerster_2003}\\
    	\vspace{0.4cm}
    	\begin{figure}
    		\centering
    		\href{https://anewage.github.io}{
    			\includegraphics[width=2cm]{resources/anewage_github_io.png}
    		}
    	\end{figure}
    \end{frame}

@@

        \begin{frame}
        \frametitle{Prologue II}
        	{\textbf{Gödel's incompleteness} theorems can be summarized as: \\
        		It is impossible to construct a theoretical language that will not \textcolor{teal}{close on itself}, with the result that there are statements that are \textcolor{teal}{undecidable} in that language.} \\
        	\vspace{0.5cm}
        	{Simply put: There are things that you \textcolor{teal}{cannot explain within a paricular language}.}

@@

    \section{Introduction}
        \subsection{Initial Notes}
            \begin{frame}{Design}
                \framesubtitle{Basics}
                The word \textcolor{teal}{design} has its roots in drawing and designation. \\
        	    \textbf{As a noun} $\longrightarrow$ From Italian \textit{\rm designò}: ``to draw''\\
        	    \textbf{As a verb} $\longrightarrow$ From Latin \textit{\rm designare}: ``to designate, to outline, to appoint''\\
        	    \centering dē- (from, out) + signō (``to mark, to sign''). 
            \begin{frame}{Design}
                \framesubtitle{Wide Range of Approaches}
        		\begin{itemize}
        			\item<1->Design as a complex but essentially \textbf{mechanical} action (e.g., some approaches in Software Engineering, Herbert Simon):\\
        			    Assuming a set of specified criteria: design is generating a set of  alternatives and assessing them against the criteria
        			\item<2-> Horst Rittle (1973) $\longrightarrow$ design is essentially for \textcolor{teal}{``wicked problems''}:
        			\textbf{no definitive formulation}, \textbf{no stopping rule}, \textbf{no assessment criteria}
        			\item<3->Latest attempts: \textcolor{teal}{examine the heart of the design activity} instead of \textcolor{red}{prescription} and \textcolor{red}{proscription}: design and cognition (e.g., most interdisciplinary attempts)
        		\end{itemize}
            \begin{frame}{Cybernetics}
                \framesubtitle{Basics}
        			\textbf{Cybernetics} (\textbackslash \textipa{saI\texttt{}b@r"netIks}\textbackslash):
        			\begin{itemize}
        				\item<1-> From Greek `kybernetes': `\textcolor{teal}{steersman}'; `kybernan': `\textcolor{teal}{to steer or pilot a ship, direct as a pilot}'
        				\item<2-> Having a goal and taking action to achieve that goal
        				\item<3-> The art of steering \cite{pangaro_web}:
        			\end{itemize}
        			\centering\includegraphics<3>[width=7.2cm]{./resources/steering1.png}
        			\centering\includegraphics<4>[width=7.2cm]{./resources/steering2.png}
        			\centering\includegraphics<5>[width=7.2cm]{./resources/steering3.png}
        			\centering\includegraphics<6>[width=7.2cm]{./resources/steering4.png}
        			\centering\includegraphics<7>[width=7.2cm]{./resources/steering5.png}
        			\centering\includegraphics<8>[width=7.2cm]{./resources/steering6.png}
        			\centering\includegraphics<9>[width=7.2cm]{./resources/steering7.png}
        			\centering\includegraphics<10>[width=7.2cm]{./resources/steering8.png}
        			\centering\includegraphics<11>[width=7.2cm]{./resources/steering9.png}
        			\centering\includegraphics<12>[width=7.2cm]{./resources/steering10.png}
            \begin{frame}{Cybernetics}
                \framesubtitle{Approaches}
        		\begin{itemize}
        			\item<1-> \textcolor{teal}{Control}, \textcolor{teal}{feedback}, \textcolor{teal}{communication}, \textcolor{teal}{circular causality} $\longrightarrow$ from N. Wiener and the transdisciplinary endeavours at Macy Conferences (1946-1953):\\
        		    Many many forms -- applications in engineering, management, law, business, ...
        			\item<2-> When applied recursively to examine cybernetic ideas and institutions $\longrightarrow$ \textcolor{teal}{The cybernetics of} \textbf{\textcolor{teal}{observing}} (rather than \textcolor{orange}{observed}) systems: Second-Order Cybernetics\\
        			\textcolor{teal}{Constructive}, \textcolor{teal}{recursive}, and \textcolor{teal}{consistent} approach to cybernetics
        			\item<3-> Important figures and institutions: Kenneth Boulding, Margaret Mead, Heinz von Foerster, Gordon Pask, Humberto Maturana, Paul Pangaro, American Society for Cybernetics, International Society for the Systems Sciences
        		\end{itemize}
            \begin{frame}{Cybernetics}
                \framesubtitle{Types of Systems}
        		\begin{figure}
        		    \centering
        		    \includegraphics[height=0.8\textheight]{resources/systems.PNG}
        		\end{figure}
            \begin{frame}{Cybernetics}
                \framesubtitle{Systems and Interactions}
        		\begin{figure}
        		    \centering
        		    \includegraphics[height=0.8\textheight]{resources/interaction.PNG}
        		\end{figure}
    \section{Considerations}
        \subsection{Design}
            \begin{frame}{Design}
                From this perspective, design is:
                \begin{itemize}
                    \item<1-> Not the outcome of a process.
                    \item<2-> Not a problem solving process.
                    \item<3-> Not a way of facing complexity.
                    \item<4-> An \textcolor{teal}{activity} that is carried out in the face of very complex and conflicting requirements.
                \end{itemize}
        \subsection{First-Order Cybernetics}
            \begin{frame}{Control}
                \begin{itemize}
                    \item<1-> Control \neq Restriction
                    \item<2-> Control = Guide towards better performance
                    \begin{itemize}
                        \item Goal or Intention
                        \item Means of communication of \textcolor{teal}{the intention} and \textcolor{teal}{the action of control} to an actor
                    \end{itemize}
                    \item<3-> What constitutes control in a system that \textcolor{teal}{enables} rather than \textcolor{red}{restricts}?
                \end{itemize}
            \begin{frame}{Law of Requisite Variety (First Law of Cybernetics)}
                \begin{itemize}
                    \item<1-> Variety = the number of all possible states for a system
                    \item<2-> Ross Ashby's law of \textcolor{teal}{Requisite Variety}: \\
                        The system that is in control must have at least as many states as the system to be controlled.
                    \item<3-> Not being restrictive $\longrightarrow$ The controller must have requisite variety.
                \end{itemize}
            \begin{frame}{Back to Control}
                \begin{columns}
                    \column{0.6\textwidth}
                        \begin{itemize}
                            \item<1-> In circular systems, which element controls and which is being controlled?
                            \item<2-> Control is \textcolor{red}{neither} in one element \textcolor{red}{nor} the other; it \textcolor{teal}{emerges} as a result of their \textcolor{teal}{interaction}.
                            \item<3-> Circularity is embodied in the role of the observer in cybernetic systems:\\
                            $\longrightarrow$ The observer cannot be inactive, or there would be no system.
                        \end{itemize}
                    \column{0.4\textwidth}
                    \begin{figure}
        		        \centering\includegraphics[height=0.6\textheight]{resources/thermostate.PNG}
        		    \end{figure}
                \end{columns}
        \subsection{Circularity and Second-Order Cybernetics}
            \begin{frame}{Subject/Metasubject}
                \begin{columns}
                    \column{0.5\textwidth}
                        \begin{itemize}
                            \item<1-> Mathematics:\\
                                A Distinct field worthy of consideration in its own right and by its own criteria.\\
                                Its \textcolor{teal}{abstraction} $\longrightarrow$ when applied to other subjects, \textcolor{teal}{casts light} upon them and \textcolor{teal}{enhances} our understanding.
                            \item<2-> Cybernetics $\sim$ Mathematics\\
                                Second-Order Cybernetics $\longrightarrow$ It is both its own subject and its own metasubject.
                            \item<3-> Design $\sim$ Cybernetics\\
                                Studied in the light of its own criteria:\\
                                (recursive) design of design
                        \end{itemize}
                    \column{0.5\textwidth}
                        \begin{itemize}
                            \item<4-> Cybernetics: \textcolor{teal}{structure} and \textcolor{teal}{form} to construct \textcolor{orange}{individual} meaning and understanding\\
                                Leaves \textcolor{teal}{meaning} and \textcolor{teal}{emotion} to the observer (\textcolor{red}{private})\\
                                $\longrightarrow$ Supports structures that support our \textcolor{teal}{autonomy} and \textcolor{teal}{freedom}\\
                                $\longrightarrow$ (recursive) \textcolor{teal}{Support of support}
                        \end{itemize}
                \end{columns}
            \subsubsection{Subjective/Objective}
                \begin{frame}{Subjective/Objective}
                    \framesubtitle{Observer Incorporated? \cite{vonFoerster_2003}}
                    \begin{columns}
                        \column{0.7\textwidth}
                            \begin{itemize}
                                \item<1-> Feedback $\longrightarrow$ an active actor (observer)
                                \item<2-> A description (observation) $\implies$ a describer (observer)
                                    \begin{enumerate}
                                        \item Observations are \textcolor{red}{not absolute} but \textcolor{teal}{relative} to the observer's point of view (Einstein)
                                        \item Observations \textcolor{teal}{affect} the observer to obliterate her hope of prediction (Heisenberg)
                                    \end{enumerate}
                                \item<3-> A description (of the world) $\implies$ a universal reality
                                \item<4-> A description (theory) of a describer has to account the \textcolor{teal}{describer} herself and her \textcolor{teal}{expression of the description}.
                            \end{itemize}
                        \column{0.3\textwidth}
                            ``I am a liar'' -- true or false? \\
                            \begin{figure}
                				\includegraphics[height=0.5\textheight]{resources/man.png}
                			\end{figure}
                			``The reality is only my imagination'' (?)
                    \end{columns}
            \subsubsection{Recursion/Repetition}
                \begin{frame}
                    \frametitle{Recursion/Repetition}
                    \framesubtitle{Heinz von Foerster's Eigen Forms (structures, functions, objects, behaviours, and values)}
                    Tokens for stable behaviour: tokens for Eigen functions (Recursive Function Theory)\\
                    Examples:
                    \begin{itemize}
                        \item<1-> $f(x)= {{x}\over{2}} +1$\\
                            \fontsize{8}{9.2}\selectfont
                            \begin{columns}
                                \column{0.1\textwidth}
                                \column{0.4\textwidth}
                                    $\longrightarrow x_0=4$\\
                                    $\longrightarrow x_1=f(x_0) = {{4}\over{2}} + 1 = 3$ \\
                                    $\longrightarrow x_2=f(x_1) = {{3}\over{2}} + 1 = 2.5$ \\
                                    $\longrightarrow x_3=f(x_2) = {{2.5}\over{2}} + 1 = 2.25$\\
                                    $\longrightarrow x_4=f(x_3) = {{2.25}\over{2}} + 1 = 2.125$\\
                                    $\longrightarrow x_5=f(x_4) = {{2.125}\over{2}} + 1 = 2.063$\\
                                    $\longrightarrow x_{11}=f(x_{10}) = {{x_{10}}\over{2}} + 1 = 2.001$\\
                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 = \textcolor{red}{2.000}$\\
                                \column{0.5\textwidth}
                                    $\longrightarrow x_0=1$\\
                                    $\longrightarrow x_1=f(x_0) = {{1}\over{2}} + 1 = 1.5$ \\
                                    $\longrightarrow x_2=f(x_1) = {{1.5}\over{2}} + 1 = 1.75$ \\
                                    $\longrightarrow x_3=f(x_2) = {{1.75}\over{2}} + 1 = 1.875$\\
                                    $\longrightarrow x_8=f(x_7) = {{x_7}\over{2}} + 1 = 1.996$\\
                                    $\longrightarrow x_{10}=f(x_9) = {{x_9}\over{2}} + 1 = 1.999$\\
                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 = \textcolor{red}{2.000}$\\ 
                            \end{columns}
                        \item<2-> $2$ is the \textcolor{teal}{Eigen value} of $f$
                    \end{itemize}
                \begin{frame}
                    \frametitle{Recursion/Repetition}
                    \framesubtitle{Heinz von Foerster's Eigen Forms (structures, functions, objects, behaviours, and values)}
                    Tokens for stable behaviour: tokens for Eigen functions (Recursive Function Theory)\\
                    Examples:
                    \begin{itemize}
                        \item<1-> $f(g)= {{d}\over{dx}}g$\\
                            $exp=e^x \implies f(exp) = {{d}\over{dx}}exp = exp$\\
                            $\longrightarrow f(f(f(...f(f(exp))...))) = exp$\\
                        \item<2-> $exp = e^x$ is the \textcolor{teal}{Eigen function} for operator $f$
                    \end{itemize}
                \begin{frame}
                    \frametitle{Recursion/Repetition}
                    \framesubtitle{Heinz von Foerster's Eigen Forms (structures, functions, objects, behaviours, and values)}
                    Tokens for stable behaviour: tokens for Eigen functions (Recursive Function Theory)\\
                    Examples:
                    \begin{itemize}
                        \item<1-> ``This sentence has ... letters'' $\implies$ \textcolor{red}{THIRTY-ONE} or \textcolor{red}{THIRTY-THREE}\\
                        ``This sentence \textcolor{blue}{`This sentence has THIRTY-ONE letters'} has ... letters'' $\implies$ \textcolor{red}{THIRTY-ONE}\\
                        ``This sentence \textcolor{purple}{`This sentence \textcolor{blue}{<This sentence has THIRTY-ONE letters>} has THIRTY-ONE letters'} has ... letters'' $\implies$ \textcolor{red}{THIRTY-ONE} \\
                        \vspace{0.7cm}
                        \item<2-> ``This sentence consists of ... letters'' $\implies$ THIRTY-NINE \\
                        ``This sentence is composed of ... letters'' $\implies$ $\nexists$
                    \end{itemize}
                \begin{frame}{Recursion/Repetition}
                    \framesubtitle{Learning, Autopoiesis, Eigen Forms, and Ranulph Glanville's Object Theory}
                    \begin{figure}
                        \centering\includegraphics[width=0.7\textwidth]{resources/recursion.png}
                    \end{figure}
            \subsubsection{Conversation}
                \begin{frame}{Conversation Model \cite{pangaro_web}}
                    \framesubtitle{Based on Gordon Pask's Conversation Theory (1976)}
                    \centering\includegraphics<1>[page=23, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<2>[page=24, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<3>[page=25, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<4>[page=26, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<5>[page=27, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<6>[page=28, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<7>[page=29, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<8>[page=30, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<9>[page=31, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<10>[page=32, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<11>[page=33, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<12>[page=34, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                \begin{frame}{The Theory}
                    \framesubtitle{Gordon Pask's Conversation Theory (1976)}
                    \centering\includegraphics<1>[page=99, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                \begin{frame}{Mental Models \cite{dubberly2009}}
                    \centering \includegraphics[width=\textwidth]{resources/models1.PNG}
                \begin{frame}{Mental Models \cite{dubberly2009}}
                    \framesubtitle{Learning as Forming and Reforming Models}
                    \centering\includegraphics[width=0.75\textwidth]{resources/learning.PNG}
                \begin{frame}{Mental Models \cite{dubberly2009}}
                    \framesubtitle{TV dramas shape culture or culture inspire TV dramas?}
                    \centering\includegraphics<1->[width=0.75\textwidth]{resources/models4.PNG} \\
                    \centering\includegraphics<2->[width=0.25\textwidth]{resources/chickenegg.jpg}
                \begin{frame}{Mental Models \cite{dubberly2009}}
                    \framesubtitle{Agreement}
                    \centering\includegraphics[width=0.5\textwidth]{resources/models5.PNG}
                \begin{frame}{Why Conversation? \cite{pangaro_web}}
                    \centering\includegraphics<1>[page=35, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<2>[page=36, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
                    \centering\includegraphics<3>[page=37, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
    \section{The Harmony}
        \

\section{References}
	\begin{frame}[allowframebreaks]
		\frametitle{References}
		\printbibliography
	\end{frame}

\section*{Appendix}
	\begin{frame}
		\setbeamercovered{transparent}
		\frametitle{Definition(s) of Cybernetics}
		\framesubtitle{Soooo... What is Cybernetics?}
		\begin{itemize}
			\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
			--- Plato (420s-340s B.C.)
			\item<2->``Cybernetique is the art of governing or the science of government.''\\
			--- André-Marie Ampère (1775-1836)
			\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
			Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
		\end{itemize}
		\setbeamercovered{invisible}
	\end{frame}
	\begin{frame}{NOT a Conversation}
        \framesubtitle{Shannon's Model of Transmission}
        \begin{figure}
            \centering\includegraphics[width=0.8\textwidth]{resources/transmission.PNG}
        \end{figure}
        This model does not scaffold novelty, is pure mechanical, and does not support learning.
    \end{frame}
    \begin{frame}{Mental Models}
        \framesubtitle{Shaping and re-Shaping}
            \centering\includegraphics<1>[width=0.75\textwidth]{resources/models6.PNG}
            \centering\includegraphics<2>[height=0.77\textheight]{resources/models7.PNG}
    \end{frame}
